---
title: "Introduction"
author: "Annie"
date: "December 2, 2018"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to cointoss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")

library(roller)
```

## Device Rolling

The package `"roller"` is a minimal implementation for simulating tossing

a device a given number of times, and to visualize the relative frequencies

in such a series of rolles.


## Creating a `device`

The first step is to create a `"coin"` object with the function `coin()`:

```{r}

mydevice <- device()

mydevice

```

By default, `device()` creates a _fair_ coin with standard sides `1`, and 

`2`, and with probability values for each side of 0.5.

You can change the defatuls with arguments `sides` and `prob`:

```{r}

loaded <- device(sides = c('HEADS', 'tails'), prob = c(0.8, 0.2))

loaded

```

## Roll a device

Once you have defined a `"device"` object, you can use the function `roll()` to

_roll_ a device a given number of `times`. The output will be an object of class 

`"roll"`, which will contain the vector of `rolls`:

```{r}

roll100 <- roll(mydevice, times = 100)

roll100

```

The `summary()` function gives you a nice table of frequencies:

```{r}

summary(roll100)

```

## Plot of relative frequencies

You can use the function `plot()` to create a graohic with the relative 

frequencies of a series of device rolls:

```{r, fig.show='hold'}
plot(roll100)
```

