---
title: "workout01-Annie-Chen"
author: "Annie"
date: "October 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
teams <- data.frame(read.csv("C:\\Users\\Annie Chen\\Desktop\\stat133\\workout1\\data\\nba2018-teams.csv", stringsAsFactors = FALSE))
knitr::opts_chunk$set(echo = TRUE, fig.path = 'C:\\Users\\Annie Chen\\Desktop\\stat133\\workout1\\report\\')
```

```{r}
teams_s <- arrange(teams, desc(salary))
teams_s


ggplot(teams_s, aes(x=reorder(team, salary), y=salary)) +
  geom_bar(stat = "identity") + 
  coord_flip() + 
  geom_hline(aes(yintercept = mean(salary), color="red")) +
  ggtitle("NBA Teams ranked by Total Salary") +
  ylab("Salary (in millions)") +
  xlab("Team")


ggplot(teams_s, aes(x=reorder(team, points), y=points)) +
  geom_bar(stat = "identity") + 
  coord_flip() + 
  geom_hline(aes(yintercept = mean(points), color="red")) +
  ggtitle("NBA Teams ranked by Total Points") +
  ylab("Points") +
  xlab("Team")


ggplot(teams_s, aes(x=reorder(team, efficiency), y=efficiency)) +
  geom_bar(stat = "identity") + 
  coord_flip() + 
  geom_hline(aes(yintercept = mean(efficiency), color="red")) +
  ggtitle("NBA Teams ranked by Total Efficiency") +
  ylab("Efficiency") +
  xlab("Team")


#index: shoot = points3 + points2 + points1
#number of shoots, disregard the points

teams_s$shoot <- teams_s$points1 + teams_s$points2 + teams_s$points3

ggplot(teams_s, aes(x=reorder(team, shoot), y=shoot)) +
  geom_bar(stat = "identity") + 
  coord_flip() + 
  geom_hline(aes(yintercept = mean(shoot), color="red")) +
  ggtitle("NBA Teams ranked by Total Shoot") +
  ylab("Number of Shoot") +
  xlab("Team")


```

# Comments and Reflections
The sink function was a bit confusing but lab06 helped a lot./ 
It's my first time working on a project with file structure and relative paths. I have problems with sinking the txt file to lab06 folder instead of workout1 folder, so I used the complete paths. Using R script was okay, more straightforward than the paths. I took about 5 hours to complete this by myself./
One problem that I ran into was withgenerating image files by knitr. I used knitr::opts_chunk$set(echo = TRUE, fig.path = '../report/') as taught in lab05, but none were generated, so i decided to use png() introduced in lab 06.
